Using Scagnostics to find Interesting Projections of Multivariate Data

### 2018-02-14 Draft/Draft.Rmd
got some optimisation working

```{r}
library(tourr)
quartz()
col <- c(rep("#f0a800", 100), rep("#486030", 100), rep("#c03018", 100))
animate(df[,1:6], guided_tour(lda_pp(df$cl)),
        display_xy(axes="bottomleft", col=col))
```

```{r}
library(geozoo)

```

>>>>

```{r eval=FALSE}
library(tourr)
quartz()
col <- c(rep("#f0a800", 100), rep("#486030", 100), rep("#c03018", 100))
animate(df[,1:6], guided_tour(lda_pp(df$cl)),
        display_xy(axes="bottomleft", col=col))
```

```{r eval=FALSE}
numbat <- read_csv("data/numbat.csv") %>% filter(group=="A")
library(geozoo)
x <- sphere.hollow(p=2, n=2000)$points
colnames(x) <- c("x4", "x7")
x <- data.frame(x1=scale(rnorm(2000)), 
                x2=scale(rnorm(2000)), 
                x3=scale(rnorm(2000)),
                x4=scale(x[,1]), 
                x5=scale(rnorm(2000)), 
                x6=scale(rnorm(2000)),
                x7=scale(x[,2]), 
                x8=scale(rnorm(2000)), 
                x9=scale(rnorm(2000)),
                x10=scale(rnorm(2000)), group="B")
numbat <- bind_rows(numbat, x)
ggplot(numbat, aes(x=x4, y=x7, col=group)) + 
  geom_point() + facet_wrap(~group) + scale_colour_manual(values=c("#609048", "#c03018"))
write_csv(numbat, path="data/numbat_circle.csv")
```

```{r eval=FALSE}
library(tourr)
quartz()
col <- c(rep("#f0a800", 100), rep("#609048", 2100), rep("#c03018", 2000))
animate(numbat[,1:10], 
        guided_tour(lda_pp(numbat$group), search_f = search_better_random),
        display_xy(axes="bottomleft", col=col))
```
